### 2024-02-14 documentation/thesis/thesis_document.tex
.

Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
crafting a compact and mobile low-field \gls{mri} unit tailored
specifically for screening purposes. As described since 1991 low-field
\gls{mri}s have evolved into a burgeoning realm of research, showcasing
substantial promise within the field of medical technology. The endeavor
by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
potential of low-field \gls{mri} for enhanced breast screening
applications.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. This selection was made for the
following reasons:

@@

It is possible to carry out the sensor characterisation shown here for
other compatible sensors using the same procedure. Pre-configured
measurements \ref{command-line-interface} and analysis pipelines
\ref{programmable-data-processing-pipeline} are available for this
purpose.

@@

\emph{MRPCli} \ref{command-line-interface} was used to control and
record the measurement series, with the functions of the
\emph{MRPDataVisualisation} \ref{mrpvisualisation} and
\emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
\ref{software-readout-framework} being used for subsequent evaluation.
The recorded measurement series are automatically analysed using the
\emph{Programmable-Data Processing Pipeline}
\ref{programmable-data-processing-pipeline} and the results are
visualised.

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Background noise level with reference to the baseline
\item
  Histogram of the background noise level
\end{itemize}

\%\%Sensor\_noise\_evaluation\_results.csv\%\%

@@

>>>>

Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
for breast) project, \emph{Fraunhofer MEVIS} in Bremen is actively
engaged in crafting a compact and mobile low-field \gls{mri} unit
tailored specifically for screening purposes. As described since 1991
low-field \gls{mri}s have evolved into a burgeoning realm of research,
showcasing substantial promise within the field of medical technology.
The endeavor by \emph{Fraunhofer MEVIS} exemplifies the ongoing
commitment to harnessing the potential of low-field \gls{mri} for
enhanced breast screening applications.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} was taken from the respective data sheets of the
sesors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

This selection was made for the following reasons:

@@

It is possible to carry out the sensor characterisation shown here for
other compatible sensors using the same procedure. Pre-configured
measurements \ref{command-line-interface} and analysis pipelines
\ref{programmable-data-processing-pipeline} are available for this
purpose are packaged with library.

@@

For the software setup, \emph{MRPCli} \ref{command-line-interface} was
used to control and record the measurement series, with the functions of
the \emph{MRPDataVisualisation} \ref{mrpvisualisation} and
\emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
\ref{software-readout-framework} being used for subsequent evaluation.
The recorded measurement series are automatically analysed using the
\emph{Programmable-Data Processing Pipeline}
\ref{programmable-data-processing-pipeline} and the results are
visualised.

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensors internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

\begin{longtable}[]{@{}lll@{}}
\caption{Sensor noise evaluation results
\label{Sensor_noise_evaluation_results.csv}}\tabularnewline
\toprule
Symbol & Unit & TLV493D\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & Unit & TLV493D\tabularnewline
\midrule
\endhead
\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
\(\mu_{t}\) & \(\mu\)T &\tabularnewline
\(\mu_{nl}\) & \% &\tabularnewline
\(\sigma_{nl}\) & \% &\tabularnewline
\bottomrule
\end{longtable}

@@

In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
sensors, an offset can also be recognised, which is dependent on the
ambient conditions. For verification, a reference measurement of the
environment was carried out with the calibrated \emph{Voltcraft GM70}
Telsameter. This provides a \emph{real} baseline value of
\(\mu_{rev}\)=-21\(\mu\)T.
